Object-based Auditory Scenes Similarity Retrieval and Classification With Scattering Transforms

### 2016-07-09 paper/structureScene.tex
update figs

\section{Acoustic Scene Similarity}

@@

\section{Acoustic Scene Classification}
Support vector machines are large-margin binary discriminators with tunable regularization of misclassified examples.

@@

@@

>>>>

\section{Results: Acoustic Scene Similarity}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{gfx/unsupervised_test1.eps}
\caption{...}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{gfx/unsupervised_test2.eps}
\caption{...}
\end{center}
\end{figure}

@@

@@

\section{Results: Acoustic Scene Classification}
Support vector machines are large-margin binary discriminators with tunable regularization of misclassified examples.

\begin{table}
\begin{center}
\begin{tabular}{c|cc}
             & time-scattering & mfcc \\
             \hline
early int.   & XX (XX)    & XX (XX)   \\
late int.    & XX (XX)    & XX (XX)   \\
ob-closest.  & XX (XX)    & XX (XX)   \\
ob-averaged. & XX (XX)    & XX (XX)   \\
ob-weighted. & XX (XX)    & XX (XX)   \\
\end{tabular}
\caption{...}
\end{center}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{c|cc}
             & w/ log comp. & w/o log comp. \\
             \hline
early int.   & XX (XX)      & XX (XX)   \\
late int.    & XX (XX)      & XX (XX)   \\
ob-closest.  & XX (XX)      & XX (XX)   \\
ob-averaged. & XX (XX)      & XX (XX)   \\
ob-weighted. & XX (XX)      & XX (XX)   \\
\end{tabular}
\caption{...}
\end{center}
\end{table}
\subsection{Role of logarithmic compression}

@@

\section{Results: DCASE 2016}
